\documentclass[preprint]{elsarticle}
\biboptions{round, numbers}
\usepackage[latin1]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{color}
%\usepackage{setspace}
\usepackage[hyphens]{url}
\usepackage[english]{babel}
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}%PABLO: he añadido esto para que no se salga la URL por el borde
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   TITLE   %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{{\em Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources 
for Low Cost Distributed Evolutionary Computation}: Response to
Editors and changes made}

\noindent
Dear Sirs,\\

We really appreciate the opportunity you have given us for improving
our work. Please find below the changes that have been made to adapt
the paper to the requirements of the editors. In the same spirit, we
have kept the content of the resulting papers the same as the initial
paper that went through the whole revision process. 

\noindent
Yours sincerely,\\
The authors.

\section*{Changes}

\begin{enumerate}
\item The paper has been split in two different papers. Everything
  related to description of the framework and baseline results has
  been moved to \cite{2016arXiv160101607M}. This paper includes all
  content from the last version of the paper, rearranged and with some
  glue text to give it coherence. This has allowed us to greatly
  reduce the amount of text from the main paper without compromising
  its accuracy.
\item The new paper has been reduced to 12 pages. After eliminating
  all the text from which the other paper has been created and
  inserting references to it, the following additional adjustments
  have had to be made:\begin{enumerate}
  \item A reference to Baratloo's paper has been eliminated, since it
    was a previous version of another referenced paper.
  \item Original figure 6 has been eliminated, with the results
    commented on the text.
  \item Tables I and II have been merged in a single tatle.
  \end{enumerate}
\item Abstract has been reduced to 199 words from the original 292
  without compromising the succinct exposition of the problems solved
  in the paper and the main results.
\item Author's names and corresponding author has been put in the
  correct format.
\item Index terms have been deleted. 
\end{enumerate}


\bibliographystyle{IEEEtran}
\bibliography{geneura}

\end{document}
%%% Local Variables:
%%% ispell-local-dictionary: "english"
%%% End:
